### 2008-07-07 trunk/Papers/rmrs-08/introduction.tex
Just in case

However, there are certain semantic
phenomena that these robust
approaches don't capture reliably, including quantifier scope, optional
arguments,
% COMMENT: this issue about optional arguments is really too cryptic.
% Basically, there is no way for assessing by *any* learned language
% processor whether a single word form that appears in
% a number of different syntactic valencies is an example of lexical
% sense ambiguity, or they are all examples of the same sense being
% used in syntactically different ways (i.e., we have optional
% arguments).  Only hand-crafted grammars can tell you this.  So, for
% example, Bos et al (2004) would get bet(x,y) for "I bet 5 pounds",
% and bet(x,y,z) for "I bet you 5 pounds" and bet(x,p) for "I bet it's
% going to rain": I.e., the vocab of the semantic formalism is
% constructed automatically from NL word forms, and the predicate
% symbols in that automatically constructed vocab vary in (a) valency,
% and (b) the semantic dependencies represented by a given argument
% position (e.g., the second argument of "bet" in "I bet 5 pounds" is
% 5 pounds, and for "I bet it's raining" it's "it's raining".
% 
and long-distance dependencies (for instance, \cite{clark:etal:2004}
report that the parser used in \cite{bos:etal:2004} 
yields semantic dependencies from the unbounded
dependencies borne from
object extraction---e.g., {\em the man that I met\dots}---with 63\%
accuracy).
Forcing a shallow parser
to make a decision about these phenomena therefore can be a major source
of errors.  Depending on the application, it may be preferrable to
give the parser the option to 
declare itself not sufficiently informed to make the decision, and
to leave the decision open---i.e., to compute a partial semantic
representation that neither over-determines nor under-determines the
semantic information revealed by the (shallow) syntactic analysis, and
to complete the semantic information later, via inferences that
exploit information extraneous to the shallow parser.

>>>>

However, there are certain semantic
phenomena that these robust
approaches don't capture reliably, including quantifier scope, optional
arguments,
% COMMENT: this issue about optional arguments is really too cryptic.
% Basically, there is no way for assessing by *any* learned language
% processor whether a single word form that appears in
% a number of different syntactic valencies is an example of lexical
% sense ambiguity, or they are all examples of the same sense being
% used in syntactically different ways (i.e., we have optional
% arguments).  Only hand-crafted grammars can tell you this.  So, for
% example, Bos et al (2004) would get bet(x,y) for "I bet 5 pounds",
% and bet(x,y,z) for "I bet you 5 pounds" and bet(x,p) for "I bet it's
% going to rain": I.e., the vocab of the semantic formalism is
% constructed automatically from NL word forms, and the predicate
% symbols in that automatically constructed vocab vary in (a) valency,
% and (b) the semantic dependencies represented by a given argument
% position (e.g., the second argument of "bet" in "I bet 5 pounds" is
% 5 pounds, and for "I bet it's raining" it's "it's raining".
% 
and long-distance dependencies (for instance, \cite{clark:etal:2004}
report that the parser used in \cite{bos:etal:2004} yields semantic
dependencies from the unbounded dependencies borne from object
extraction---e.g., {\em the man that I met\dots}---with 63\%
accuracy).  Forcing a shallow parser to make a decision about these
phenomena therefore can be a major source of errors.  Depending on the
application, it may be preferrable to give the parser the option to to
leave the decision open when it's not sufficiently informed---i.e., to
compute a partial semantic representation that neither over-determines
nor under-determines the semantic information revealed by the
(shallow) syntactic analysis, and to complete the semantic information
later, via inferences that exploit information extraneous to the
parser.
